Analysis

### 2021-04-25 analysis.Rmd
ignore big

```{r cache = TRUE}
m2b <- brm(
  anx_s ~ age_s  + male  +  bg_within + bg_between +  (1  +  bg_within |
                                                         country),
  data = d1,
  family = "gaussian",
  seed = 1234,
  warmup = 1000,
  iter = 300,
  chains = 4,
  file = "m2_aa.rds"
)
model_parameters(m2b, test = "p_direction")
random_parameters(m2b)
```

>>>>

```{r cache = TRUE}
m2b <- brm(
  anx_s ~ age_s  + male  +  bg_within + bg_between +  (1  +  bg_within |
                                                         country),
  data = d1,
  family = "gaussian",
  seed = 1234,
  warmup = 1000,
  iter = 300,
  chains = 4,
  file = "m2_aa.rds"
)
head(m2_aa.rds)
model_parameters(m2b, test = "p_direction")
random_parameters(m2b)
```
